---
title: "DefraStats Twitter Account"
author: "David Lee"
date: "10/12/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load up required libraries
library(twitteR)
library(dplyr)
library(lubridate)
library(igraph)
library(networkD3)
library(readr)
library(here)

twitterkeys <- readRDS(here("twitterkeys", "twitterkeys.rds"))

setup_twitter_oauth(consumer_key = twitterkeys$consumer_key, 
                    consumer_secret = twitterkeys$consumer_secret,
                    access_token = twitterkeys$access_token, 
                    access_secret = twitterkeys$access_secret)

# read in helper functions
source("~/Twitter/friendsnet.R")
```

## Playing about with Twitter Data

First we need access to twitter. Then we can start to explore.


### Accessing the Twitter API

Describe how to sign up and access the twitter API to be able to get data. Now we can run some code to connect:


```{r, eval = FALSE}

# load up required libraries. twitteR only is needed, but we will use some of
# the others later.
library(twitteR)
library(dplyr)
library(lubridate)
library(igraph)
library(networkD3)
library(readr)

# read in helper functions. Not needed to connect to twitter, but we'll use
# these later.
source("~/Twitter/friendsnet.R")

# connect to twitter. Ive savedmy keys in an RDS data file so that I don't have
# to expose them in this code. Wouldn't want you stealing my keys!
twitterkeys <- readRDS("~/Twitter/twitterkeys.rds")

setup_twitter_oauth(consumer_key = twitterkeys$consumer_key, 
                    consumer_secret = twitterkeys$consumer_secret,
                    access_token = twitterkeys$access_token, 
                    access_secret = twitterkeys$access_secret)

```

### We're in!

Cool. Let's start with some exploration.

```{r, eval = FALSE}

# We get details of the DefraStats account
defrastats = getUser('DefraStats')

# Let's look at our followers
followers <- defrastats$getFollowers()
followersdf <- twListToDF(followers) # it might be easier to have this as a dataframe

# We can save this data for future analysis
write.csv(followersdf, file = "~/Twitter/defrastats.csv")

```

Let's take a look at our data.

```{r followers, echo = FALSE, results = "asis"}

followersdf <- read.csv(file = "~/Twitter/defrastats.csv", header = TRUE)

knitr::kable(head(followersdf))

```

### What can we say about our followers

Theres a fair amound of informaion here. What can we do with it?

### Networks

```{r networks, echo=FALSE}

user <- read_csv("~/Twitter/DefraStats.csv")

user <- user %>% 
        mutate(friend = "DefraStats") %>% 
        select(friend, follows = name)


folls <- read_csv("~/Twitter/DefraStats_friends.csv")
colnames(folls) <- c("friend", "follows")

all <- rbind(user, folls)

el <- count(all, friend, follows)

friend_graph <- graph_from_data_frame(d = el, directed = T)

lay <- layout_with_kk(friend_graph)
par(bg="white", mar=c(1,1,1,1))
plot(friend_graph, 
     layout = lay,
     vertex.color = "wheat3",
     vertex.size = 10,
     vertex.label.family = "sans",
     vertex.shape = "circle",
     vertex.label.color = "black",
     edge.arrow.size = 0.2,
     edge.arrow.width = 0.2)


```

Interactivity

```{r d3}

wc <- cluster_walktrap(friend_graph)
members <- membership(wc)
d3_rt <- igraph_to_networkD3(friend_graph, group = members)

forceNetwork(Links = d3_rt$links, Nodes = d3_rt$nodes, 
             Source = 'source', Target = 'target', 
             NodeID = 'name', Group = 'group', fontSize = 12, zoom = TRUE)

```
